---
title: "p8105_hw5_cy2752"
author: "Congyu Yang"
date: "2024-11-09"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      fig.width = 8, 
                      fig.height = 6,
                      out.width = "90%")
library(tidyverse)
library(purrr)
library(patchwork)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

## Problem 2

```{r}
randomset <-  function(n = 30,mu,sigma = 5) {
  
  x = rnorm(n,mu,sigma)
  
  x %>%t.test()%>% 
    broom::tidy() %>% select(estimate,p.value) %>% 
    mutate(power = ifelse(p.value < 0.05,T,F),
           mu = mu)
}

output = vector("list", 5000)
output_set <- vector("list",6)

for (j in 1:6) {
  for (i in 1:5000) {
  
  output[[i]] = randomset(mu = j)
  
  }
  output_set[[j]] <- bind_rows(output)
}
```

## Make a plot

```{r}
output_set %>%
  bind_rows() %>% 
  group_by(mu) %>% 
  summarise(prop_power = mean(power)) %>% 
  ggplot(aes(x = mu, y =prop_power)) + 
  geom_point()+geom_line()
```

As we can see, as the true value of $\mu$ going larger, the power is approaching towards 1, since we are always doing the test comparing if the mean is equal to 0, so as the true mean moves away from 0, the power of the test is getting higher.

```{r}
mu_compare_all <- output_set %>%
  bind_rows() %>% 
  group_by(mu) %>% 
  summarise(avg_estimate = mean(estimate)) %>% 
  ggplot(aes(x = mu, y =avg_estimate)) + 
  geom_point()+geom_line()+
  xlim(0,7)+ ylim(0,7)

mu_compare_only_reject <-output_set %>%
  bind_rows() %>% 
  filter(power == T) %>% 
  group_by(mu) %>% 
  summarise(avg_estimate = mean(estimate)) %>% 
  ggplot(aes(x = mu, y =avg_estimate)) + 
  geom_point()+geom_line()+
  xlim(0,7)+ ylim(0,7)

mu_compare_all + mu_compare_only_reject
```

The sample average of $\hat{\mu}$ across tests for which the null is rejected is not equal to(larger than) the true value of $\mu$ when the $\mu$ is smaller, but as $\mu$ getting far away from 0, they are getting closer and equal to each other.\

This is because our test is about whether $\mu$ = 0, so when we do this test on small $\mu$, samples $\hat{\mu}$ across tests for which the null is rejected are far away from 0, so it will also be away from the true value of $\mu$.\

While for larger $\mu$, almost all samples have their null hypothesis rejected, so it is actually compare the average of all estimate of $\hat{\mu}$ and the true value of $\mu$, accordingly, sample average of $\hat{\mu}$ across tests for which the null is rejected is equal to the true value of $\mu$ when $\mu$ gets far away from 0.

# Problem 3

```{r}
homicide <- read_csv("data/homicide-data.csv") %>% 
  mutate(city_state = str_c(city,state,sep = ", "))

total_homicide <- homicide %>% 
  group_by(city_state) %>% 
  summarize(total_cases = n()) 

unsolved_homiside <- homicide %>% 
  filter(disposition == "Closed without arrest" | disposition == "Open/No arrest") %>% 
  group_by(city_state) %>% 
  summarize(unsolved_cases = n()) 

(cases_table <- left_join(total_homicide,unsolved_homiside, by = "city_state") %>% 
    mutate(
    unsolved_cases = case_when(is.na(unsolved_cases) ~ 0,TRUE ~ unsolved_cases)
    ))
  
```
This dataset about homicides in 50 large U.S. cities has `r nrow(homicide)` rows and `r ncol(homicide)` columns. It has more than 52000 criminal homicides over the past decade. And it includes the date of the cases，basic information about the suspect，location of the cases and whether the arrest has been made.

```{r}
BalMD <- cases_table %>% 
  filter(city_state == "Baltimore, MD")

prop_test_BalMD <-
  prop.test(x = BalMD %>% pull(unsolved_cases), n = BalMD %>% pull(total_cases)) %>%
  broom::tidy() %>% 
  select(estimate,conf.low,conf.high) %>% 
  mutate(city = BalMD %>% select(city_state)) %>% 
  unnest()

est_and_CI <- function(state){
  
  City <- cases_table %>% filter(city_state == state)
  
  prop.test(x = City %>% pull(unsolved_cases), n = City %>% pull(total_cases)) %>%
  broom::tidy() %>% 
  select(estimate,conf.low,conf.high) %>% 
    mutate(city = City %>% select(city_state)) %>% 
  unnest()
  
}


prop_test_all <- map_dfr(cases_table %>% pull(city_state), \(x) est_and_CI(x))

```

```{r}
prop_test_all %>% 
  arrange(desc(estimate)) %>% 
  mutate(city_state = reorder(city_state, estimate)) %>%
  ggplot(aes(x = city_state, y = estimate)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
    geom_point()+
  theme(axis.text.x = element_text(size = 5,angle = 30))
  
  
```
